A new metric for automatic discovery of periodic patterns in time series

### 2021-03-09 paper/main.Rmd
table updated and theme of raw plot

elec_zoom <-  elec %>%
  as_tibble() %>% 
  dplyr::filter(date(date_time) > as.Date("2019-09-01") & date(date_time) < (as.Date("2019-09-30"))) %>%
  ggplot(aes(x=date_time, y = kwh)) +
  #geom_point(size = 0.1, colour = "black", alpha = 0.3) +
  geom_line(size = 0.1, colour = "blue", alpha = 0.6) +
  facet_wrap(~id, 
             scales = "free_y",
             ncol = 1,
             strip.position =  "right",labeller = "label_both") + xlab("Time [30m]") + 
  theme_minimal() + 
  ylab("linear energy demand (kwh) for September") + ggtitle("b")

heatplot +  facet_grid(id~.) + elec_zoom +
  theme(
    strip.background = element_blank(),
    strip.text.y  = element_blank(), plot.margin = unit(c(0, 0, 0, 0), "cm")) +
  plot_layout(widths = c(1, 2))

@@

```{r tab-rank-8}
elec_rank <- elec_sig_split %>% 
  select(-c(6,7, 9, 10)) %>% 
  pivot_wider(
              names_from = id,
                values_from = rank) %>% 
  rename("facet variable" = "facet_variable",
         "x variable" = "x_variable",
         "facet levels" = "x_levels",
         "x levels" = "x_levels")

>>>>

elec_zoom <-  elec %>%
  as_tibble() %>% 
  dplyr::filter(date(date_time) > as.Date("2019-09-01") & date(date_time) < (as.Date("2019-09-30"))) %>%
  ggplot(aes(x=date_time, y = kwh)) +
  #geom_point(size = 0.1, colour = "black", alpha = 0.3) +
  geom_line(size = 0.1, colour = "blue", alpha = 0.6) +
  facet_wrap(~id, 
             scales = "free_y",
             ncol = 1,
             strip.position =  "right",
             labeller = "label_both") + 
  xlab("Time [30m]") + 
  theme_grey() + 
  ylab("linear energy demand (kwh) for September") + ggtitle("b")

heatplot +  facet_grid(id~.) + elec_zoom +
  theme( plot.margin = unit(c(0, 0, 0, 0), "cm")) +
  plot_layout(widths = c(1, 2))

@@

```{r tab-rank-8}
elec_rank <- elec_sig_split %>% 
  select(-c(6,7, 9, 10)) %>% 
  pivot_wider(
              names_from = id,
                values_from = rank) %>% 
  rename("facet variable" = "facet_variable",
         "x variable" = "x_variable") %>% 
  select(-facet_levels, -x_levels)
